---
title: CitRad - read and display raw spectrum data
---

```{r knitr settings, echo=F, include=F}
knitr::opts_chunk$set(echo=T, cache=F, warning =F, message = F, error = F)
```

Load the necessary libraries:

```{r libraries and helper functions}
library(plyr)
library(dplyr)
library(viridis)
library(lubridate)
source("functions.R")
```


## read data

To read the raw data use the `read_binary_file_8bit()` function located in `functions.R`. 

```{r read data, results='hide'}
filename <- "../../../data/SD-Card/2024-03-29_Nordring/rawdata_2024-3-29_12-8-50.BIN"
data_list <- read_binary_file_8bit(filename)
#rm(data, file_version, iq_measurement, n, num_fft_bins, size, start_time, timestamps, sample_rate)
attach(data_list)
```

The `attach()` command puts all variables in data_list in the global environment.


## conversion between frequency and speed

The FFT bins go from 1 to 1024. Bin 512 is 0 km/h. The upper bins represent positive speeds, lower bins negative speed (movement in the opposite direction). The conversion factor between frequency and speed is the following:

$$\frac{sample\_rate}{1024}/44.0 \approx 0.266$$
with $sample\_rate = `r sample_rate`$


```{r speed conversion, echo=T}
speed_conversion = (sample_rate/1024)/44.0
speeds <- (1:1024-512) * speed_conversion
```

In preparation for the plots we also do some timestamp conversion:

```{r timestamp conversion}
timestamps_date <- start_time + milliseconds(timestamps)
timestamp_minutes = timestamps/1000/60
```

# plot spectrum

```{r plot with timestamp}
index <- 19585+0:1000
image(timestamp_minutes[index], speeds,  data[index,], col=magma(100), main="spectrum")
```

To speed up the generation of the spectrum plot (especially for large timeframes) we can use the option `useRaster = T`:


```{r plot faster with index}
image(index, speeds,  data[index,], col=magma(100), useRaster = T, main="spectrum")
```

Since `useRaster` needs a regular x-axis we can't use the timestamp, since that one is a bit irregular depending on the processing speed of the Teensy:

```{r timestamp irregularities}
diff(timestamps) %>% unique %>% sort
```

To add back some sensible x-axis:

```{r plot with tick labels}
tick_positions <- seq(min(index), max(index), length.out=10)
tick_labels <- (start_time + minutes(round(timestamp_minutes[tick_positions]))) %>% with_tz("CET") %>%
  format("%Y-%m-%d\n%H:%M:%S %Z") %>% paste(., "\n", round(tick_positions))

image(index, speeds,  data[index,], col=magma(100), useRaster = T, xaxt="n", xlab="", main="spectrum")
axis(1, tick_positions, tick_labels, mgp=c(4, 2.5, 0))
```

We can also limit the speeds to the expected range and add some grid lines:

```{r speed selection and grid lines}
speed_selection <- which(abs(speeds)<=70)
image(index, speeds[speed_selection],  data[index,speed_selection], col=magma(100), useRaster = T, xaxt="n", xlab="", main="spectrum")
axis(1, tick_positions, tick_labels, mgp=c(4, 2.5, 0))
abline(h=-7:7*10)
```

# write plot to file:

We create a graphics folder first:

```{r create graphics folder}
dir.create("Grafiken")
```

And then render a graphic for the whole timeline into a png file:

```{r export png}
system.time({ # tells us the processing time it took
  
# calculate pixel width with 200 pixels per minute:
timerange_minutes <- diff(range(timestamp_minutes))
pixel_width <-  round(timerange_minutes) * 200

# pepare axis with 1 tick per minute:
index <- 1:length(timestamps)
tick_positions <- seq(min(index), max(index), length.out=timerange_minutes)
tick_labels <- (start_time + minutes(round(timestamp_minutes[tick_positions]))) %>% with_tz("CET") %>%
  format("%Y-%m-%d\n%H:%M:%S %Z") %>% paste(., "\n", round(tick_positions))


filename = paste0("./Grafiken/", as.numeric(Sys.time()), ".png")
# open graphic device:
png(filename, height = 500, width = pixel_width)

# create graphic
image(index, speeds[speed_selection],  data[index,speed_selection], col=magma(100), useRaster = T, xaxt="n", xlab="", main="spectrum")
axis(1, tick_positions, tick_labels, mgp=c(4, 2.5, 0))
abline(h=-7:7*10)

# close graphic device
dev.off()

})
```



In my experience the fastest way to display big spectrum image files is in the browser (like Firefox or Chrome).
